Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-13 rates-neurips-21/rates.tex
slight addition of comments

\paragraph{Surrogate regret bounds.}
Given a target problem, we would like to design surrogates which efficiently solve it.
A standard tool to establish this efficiency is a \emph{surrogate regret bound}.
We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
\bo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$.}
(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
The \emph{target regret} of $h$ is thus $R_\ell(\psi\circ h;\D) = E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.

@@

\bo{I think the discussion I had on sqrt and fast rates would be useful...}

>>>>

\paragraph{Surrogate regret bounds.}
Given a target problem, we would like to design surrogates which efficiently solve it.
A standard tool to establish this efficiency is a \emph{surrogate regret bound}.
We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = \E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} \E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
\bo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$. Replaced E with expectation symbol.}
(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
The \emph{target regret} of $h$ is thus $R_\ell(\psi\circ h;\D) = \E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} \E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.

@@

\bo{I think the discussion I had on sqrt and fast rates would be useful...also the notation of $m$ data points and a hypothesis $\hat{h}_m$, and $\hat{g}_m = \psi \circ \hat{h}_m$.}
